---
title: <span class="fragment roll-in">I Am <strong><font color = 'red'>Angus</font></strong></span><br><span class="fragment roll-in"><strong><font color = 'red'>Are</font> You?</span></strong>
author: <span class="fragment roll-in">Alex Bresler</span>
date: <small><span class="fragment roll-in"><font color = 'red'>Sports Illustrated</font> Hackathon </span><span class="fragment roll-in">May 16, 2015</span></small>
output:
  revealjs::revealjs_presentation:
    transition: slide
    highlight: monochrome
    self_contained: false
    
---

# Few Words About Me


## I am {a | an}:

<center><div class = "fragment roll-in"><img src = "images/asb.jpg" height = "200" width = "200"></div></center>
<ul>
<li class="fragment roll-in"><strong><font color = 'red'>Self Taught Coder and Data Scientist (circa 2010)</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Data Visualization Fanatic</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Impassioned Data Explorer</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Angel Investor</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Sports Fan</font></strong></li>
<ul>

# Enough About Me

## Angus MacGyver

<iframe class = 'fragment roll-in' width="640" height="500" src="https://www.youtube.com/embed/UKTNWI0eYJ4" frameborder="0" allowfullscreen></iframe>

## MacGyver

<blockquote class = 'fragment roll-in'>
<p><strong><i>adj.</i></strong><br>One who performs<strong><font color = "blue"> great feats of ingenuity</font> on a <font color = "red">moments notice</font>.</strong></p>
</blockquote>

## Someone Who..

<ul>
<li class="fragment roll-in">Possesses <strong><font color = 'blue'>Superior Analytical Skills</font></strong></li>
<li class="fragment roll-in">Is Able to <strong><font color = 'blue'>Decompose</font></strong> and <strong><font color = 'blue'>Solve Complex Problems</font></strong></li>
<li class="fragment roll-in">Is <strong><font color = 'blue'>Extremely Resourceful</font></strong></li>
<li class="fragment roll-in">Understands <strong><font color = 'blue'>What People Want</font></strong></li>
<li class="fragment roll-in">Can <strong><font color = 'blue'>See What Others May Not</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'blue'><p class = "fragment grow">Can Turn What We Have </font><font color = 'red'>Into What We Need</font></p></strong></li>
</ul>

## <small>Our SAK {Swiss Army Knife}</small>

<img class = "fragment roll-in" src = "images/ds_mcGuyver.svg">

## Mac Hacking

<ul>
<li class="fragment roll-in"><strong><font color = 'red'>Find the data</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Clean the data</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Resolve the data</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Visualize the data</font></strong></li>
</ul>

##<small>A Mac Hack Example</small>
<div class = "fragment roll-in">
Who was this McGyver guy?
</div>

## Boom

```{r, echo=FALSE,autodep=FALSE,warning=FALSE,tidy=FALSE,cache.comments=FALSE,cache=FALSE,results='hide',include=FALSE}
macgyver_me <- function(){
	packages <- 
	c('magrittr', 'dplyr', 'rvest', 'qdap', 'tidyr', 'stringr', 'stringi', 'tm', 'readr', 'wordcloud')

lapply(packages, library, character.only = T)

	mac.stuff <- 
	read_csv('data/mac.csv')
mystopwords <- 
	c(stopwords('english'),"used","with", 'made')

tdm <- 
	mac.stuff %>% 
	DataframeSource %>% 
	Corpus %>% 
	tm_map(function(x)removeWords(x,mystopwords)) %>% 
	TermDocumentMatrix


m <- 
	tdm %>% 
	as.matrix()
v <- 
	m %>% 
	rowSums %>% 
	sort(decreasing=TRUE)

d <- 
	data.frame(word = names(v),freq=v)

wordcloud(d$word,d$freq, scale=c(4,.2), max.words=300, random.order=FALSE, rot.per=0.15, use.r.layout=TRUE, colors=wesanderson::wes_palette('Zissou'))
}
```

```{r, echo=TRUE,message=FALSE, warning=FALSE, fig.width = 8, fig.height = 4.5}
macgyver_me()
```

## Great Escape

<iframe  class = 'fragment roll-in'width="640" height="390" src="https://www.youtube.com/embed/LTWEh2mcdsg" frameborder="0" allowfullscreen></iframe>

# <small>Professional Sports, The World's Glue</small>

## <small>But Why</small>
<ul>
<li class="fragment roll-in"><strong><font color = 'red'>Brings People Together</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Experience Enhanced by Technology</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>Draws the Largest Television Audience</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'red'>The Largest Proportion of Daily Google and Twitter Trends</font></strong></li>
<li class="fragment roll-in"><strong><font color = 'blue'><p class = "fragment grow">To Name Just a Few!!</p></font></strong></li>
</ul>


## <small>Where Else Does This Happen??</small>
<div class = "fragment roll-in">
<img src = "images/1390491377_airbargs.gif">
</div>

## <small>Or This..</small>
<div class = "fragment roll-in">
<img src = "images/DownrightSkeletalAustraliansilkyterrier.gif">
</div>

##<small>Where Mom's Get This Into Rivalry</small>
<div class = "fragment roll-in">
<img src = "images/LEGOOOOOOOOOO.gif" width = "400">
</div>


##<small>Where Two Grown Men Can Truly Let Loose and Get Down</small>
<div class = "fragment roll-in">
<img src = "images/whiteguydance.gif">
</div>

##<small>Where Superstition Takes On a Life Of It's Own</small>
<div class = "fragment roll-in">
<img src = "images/manny.gif" width = "400">
</div>


##<small>Where Magicians Perform Real Magic</small>
<div class = "fragment roll-in">
<img src = "images/messi.gif">
</div>

##<small>Where David Can Beat Goliath</small>

<div class = "fragment roll-in">
<img src = "images/go-white-boy_medium.gif" width = "400">
</div>

#<small>Let's Look at Some Sports Mac Hacks</small>

##<small>To Unite the State of .....</small>
<iframe  class = 'fragment roll-in' width="700" height="600" src="statebins/index.html" frameborder="0" allowfullscreen></iframe>


##<small>To Show the Evolution of NFL Lineman</small>

##<small>One More</small>

# Conclusion


